---
title: "Targeting Okalhoma's 5th District in Renewable Energy"
author: "Nikole Vannest, Cat Takata, Ethan Hoffman"
date: "1/27/2021"
output:
  pdf_document: default
  word_document: default
---


1. Policy Campaign: **Ready for 100**. We are oppoosing renewable energy and siding with our conservative counterparts. 



2. Member of Congress: **Rep. Kendra Horn (D)** - Oklahoma District 5, 2018-2020

By manipulating the data variables consistent with renewable energy: "fundrenewables", drilloffshore", "discussOppose", and  Representative Kendra Scott (D) was isolated because of her progressive and centre position on select issues. By identifying her progressive stance, especially within Oklahoma's majorily conservative 5th District, we knew she did not align with the majorty of her constituents. Public opinion could pivot support for an environmental campgain as well as hers. In the interest of fun, we supoort the "anti-environmental" audience in order to remove Rep Horn or convince her to oppose the policy.  


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

## Packages ----

library(dplyr) #for data wrangling
library(readxl) #for reading Excel file
library(tidyverse) #for dataframe functions
library(janitor) #for renaming variables
library(ggplot2) #for plotting
library(stringr) #for text manipulation
library(here)

`%nin%` = Negate(`%in%`)

## Reading data ----

#reading datasets:
#note: this will only work without changing the paths if you open the .Rproj file
data <- read.csv(here("data","congress_116_data.csv"))
metadata <- read.csv(here("data", "Combined_Metadata.csv"))
```

```{r, data carpentry}
#reordering metadata 'variable' to match variable order in 'data':
order <- match(names(data),metadata$variable)
metadata <- metadata[order,]

## Data filtering and visualization to examine electoral vulnerability ----

#selecting for vulnerable House members:
vulnerable <- data %>%
  filter(primary_percent < 0.6 | general_percent < 0.6)
```

```{r, exploratory graphs, include = FALSE}
## Data filtering and vizualization to examine vulnerability and opinion ----

#selecting Democrats vulnerable to primary challenges who are not strongest possible environmentalists:
vulnerableD <- data %>%
  filter(primary_percent < 0.6 & party == "D" & lcv_score<100)

#plotting the distribution of LCV scores vs. constituent support to address climate:
ggplot(vulnerableD, aes(x=lcv_score, 
                       y= congress)) + 
  geom_point() +
  geom_text(aes(label=district_id),
            hjust=0, vjust=0) +
  ggtitle("LCV Scores of vulnerable Dems compared to \nproportion of constituents that want more action from Congress")


```

```{r, Final visual}
# Subsetting data to focus on Oklahoma district 5 and select variables

library(reshape2)

Kendra <- vulnerableD %>% 
  filter(candidate_name == "Horn, Kendra",)

Kendra_melt <- Kendra %>% 
  mutate(general_percent = general_percent*100) %>% 
  select(general_percent, discussOppose, drilloffshore, mediaweeklyOppose, 
         timingOppose, priority) %>% 
  melt()

# Table showing data from Kendra df

#Bar plot showing constituent support for certain issues
ggplot(Kendra_melt, aes(x = value)) + 
  geom_col(aes(y = variable), fill = "red") +
  labs(y = c(), x = "Percent population",
       title = "Oklahoma's 5th District Public Perception of Global \n Warming as a Threat") +
  scale_y_discrete(labels = c("Horn Win Margin", "GW not discussed", "Pro Offshore Drilling", "Lack of Media Attention", "Poor Timing", "Global Warming Important")) +
  theme_minimal()
  

```


3. Key Public Audience

The oil and natural gas drilling industry of Oklahoma’s 5th Congressional District is a pivotal audience in determining support, or lack thereof, for the Ready for 100 campaign. Rep. Kendra Horn’s moderately progressive stance does not fully align with her majority conservative constituents; public opinion would urge her to oppose. As a member of the House Committee on Science, Space, and Technology, and a 83.32% estimated percentage for support funding research into renewable energy sources, Horn would be more inclined to introduce electrical and solar energy technology to reach clean energy standards. Key district stakeholders such as Devon Energy and Chesapeake Energy and Continental Resources along with the rest of the district’s heavily influenced drilling industry are threatened by this transition as it jeopardizes jobs and the districts’ financial livelihood. 

Rep Horn’s 1.4 percentage points defeat over incumbent Rep. Steve Russell (R) and LCV score of 93 does not warrant incumbency for the next election. This small portion of voters could easily be swayed to replace Rep Horn in the next election. A more conservative candidate focused on maintaining jobs within the drilling industry and not pursuing progressive climate change policy would have more success with Oklahoma’s 5th District constituents. 


4. Political Advertisement

The Reject Ready for 100 campaign will create television and print ads to reach its constituents, many of whom work in the oil and natural gas industry, and will be affected by Ready for 100 if it's implemented in Oklahoma.

**Political Ad:**
Oil and natural gas workers and their families are deeply concerned about Kendra Horn's support for Ready for 100, the clean energy campaign that will hurt Oklahoma's booming industries. Clean energy initiatives will affect our state's workers, their families, and their communities' livelihood by forcing oil and natural gas workers out of their jobs, and replacing them with new "clean" technology to mobilize a "clean energy revolution", putting many Oklahomans at risk of falling into poverty within the next decade and increasing customers' utility bills.

Tell Kendra Horn: Protect our Workers, Protect their Jobs, Reject Ready for 100.


**References for Section 3 (Key Public Audience)**

Ballotpedia - Oklahoma 5th Congressional District 2020 Election: https://ballotpedia.org/Oklahoma%27s_5th_Congressional_District_election,_2020

Ballotpedia - Kendra Horn: https://ballotpedia.org/Kendra_Horn

Ballotpedia Stephanie Bice: https://ballotpedia.org/Stephanie_Bice

Census Reporter Congressional District 5, OK: https://censusreporter.org/profiles/50000US4005-congressional-district-5-ok/

Reuters - Oklahoma Oil Bust Article :https://www.reuters.com/investigates/special-report/usa-oklahoma-bust/

U.S. Census Bureau - My Congressional District - Oklahoma District 5: https://www.census.gov/mycd/?st=40&cd=05

AMP Research Lab - My District 2020: https://www.apmresearchlab.org/representingus/2020profiles#my-district